Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-09 ccppabc/text/revision/main.tex
Significant edits to @MJV's addition to address Ref Report comment 2,3 Issues #15 and #17; *edits are incomplete

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). 
}
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect and especially incorrect for the GMF observable case.
}
{\bf \color{dred}
In the case where the observable $\gmf(N)$ is used as a summary statistic
of a galaxy catalog, assuming a Gaussian functional form for the likelihood
would clearly misreprenset the true likelihood function. In fact, this 
discrepancy may explain the less biased constraints on $\alpha$ from the ABC-PMC analysis 
compared to the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}{\bf \color{darkgreen} @CHH : added $\alpha$ to the previous sentence since the other constraints our consistent!}

{\bf \color{dred} It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC. Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects. This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a signal-to-noise ratio cut.}

{\bf \color{dred} In standard likelihood analyses, these selection effects, if not accounted for, can lead to biases in the inferred parameters of interest. Methods that rely on a likelihood function may not correctly predict how the functional form of the likelihood is impacted by the presence of possible selection effects and systematic uncertainties.  
%Hierarchical models can modify the likelihood functions through by %taking into account the selection effects. 
Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the simulated data that incorporates signal-to-noise ratio cuts, incompleteness, systematic uncertainties etc. }{
\bf \color{darkgreen} MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ? }
%%%

%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.

>>>>

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). 
}
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect for 2PCF.
}
{\bf \color{dred}
In the case where the observable $\gmf(N)$ is used as a summary statistic
of a galaxy catalog, assuming a Gaussian functional form for the likelihood
clearly misrepresents the true likelihood function. This incorrect likelihood, 
may explain why the constraints on $\alpha$ are less biased for the ABC-PMC analysis 
than the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}

{\bf \color{dred} 
Although in our comparison using simple mock observations, we find generally 
consistent parameter constraints from both the ABC-PMC analysis and the standard 
Gaussian pseudo-likelihood analysis, more realistic scenarios face mmany factors
that can generate inconsistencies. Consider a typical galaxy catalog from 
observations for LSS. These catalogs consist of objects with different data 
qualities, signal-to-noise ratios, and systematic effects. For example, catalogs 
are often incomplete beyond some luminosity/redshift or have some threshold 
signal-to-noise ratio cut imposed on them.
}

%It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC.  Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects.  This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a signal-to-noise ratio cut.
{\bf \color{dred} 
These selection effects, coupled with the systematic effects mentioned above, 
make correctly predicting the functional form of the likelihood difficult. 
In the standard Gaussian pseudo-likelihood analysis, and other analysis that
depend on writing down a likelihood function, these effects can siginficantly 
bias the inferred parameters of interest. In these situations, employing
ABC equipped with a generative forward model that incorproates selection and 
systematic effects may produce less biased parameter constraints. 
}
%Methods that rely on a likelihood function may not correctly predict how the functional form of the likelihood is impacted by the presence of possible selection effects and systematic uncertainties.  
%Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the simulated data that incorporates signal-to-noise ratio cuts, incompleteness, systematic uncertainties etc. }{
%\bf \color{darkgreen} MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ? }
%%%
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.
